---
title: 'Data607: Project3 Database Setup and Testing'
output: html_document
params:
  dbusername: 
    label: "username"
    value: ""
    input: text
  dbpassword: 
    label: "password"
    value: ""
    input: password
  dbschema: 
    label: "schema"
    value: ""
    input: text
  dbhost:
    lable: "host"
    value: ""
    input: text
---

Overview: user will be prompted to provide valid credentials for MySQL database connection to write to correct schema and then create tables

#### Load libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(jsonlite)
library(RMySQL)
```

## Load data storage in Github

```{r load_file_paths}
indeed_fp = 'https://raw.githubusercontent.com/beninbar/Team_Science/master/data/Indeed_tagged.csv'
indeed_json = 'https://raw.githubusercontent.com/Anthogonyst/Team_Science/master/data/indeed_job_description_data.json'
linkedin_fp = 'https://raw.githubusercontent.com/beninbar/Team_Science/master/data/LinkedIn_tagged.csv'
linkedin_json = 'https://raw.githubusercontent.com/Anthogonyst/Team_Science/master/data/job_description_data.json'

```

#### Load data from Github Repo files

```{r load_files_into_R}
indeed_jds <- read_json(indeed_json, simplify=TRUE)
linkedin_jds <- read_json(linkedin_json, simplify=TRUE)
indeed_keywords <- read_csv(indeed_fp)
linkedin_keywords <- read_csv(linkedin_fp)

```

#### Load database connection for local host:

```{r connect_to_db}
local_db <- dbConnect(MySQL(), user=params$dbusername, password=params$dbpassword, dbname=params$dbschema, host=params$dbhost)

```


#### Prepare and union job description data from both sources

```{r}
linkedin_jds <- linkedin_jds |> mutate(jobdesc_id = row_number(), 
                                       job_description='Data Scientist',
                                       source='LinkedIn')
indeed_jds <- indeed_jds |> mutate(jobdesc_id=row_number(), source='Indeed')
jds <- union_all(linkedin_jds,indeed_jds) |> rename(job_title=job_description,employment_type=`Employment type`,seniority_level=`Seniority level`,industries=Industries,job_function=`Job function`,company_name =company)


```

#### Prepare input tables for database write process

```{r}
company_info_input <- jds |> group_by(company_name) |> summarise(cnt=n()) |> mutate(company_id = row_number()) |> select(company_id, company_name)

company_data <- jds |> left_join(company_info_input,by='company_name')

final_jds <- company_data |> select(jobdesc_id,source,job_title,company_id,link,location,employment_type,job_function,salary,seniority_level) 

company_info <- company_data |> select(company_id,company_name,industries) |> arrange(company_id) |> group_by(company_id,company_name) |> mutate(industry_group = paste(industries,collapse='|')) |> distinct(company_id,company_name,industry_group)

```


#### Prepare the keywords tagged for database writing

```{r prepare_validate_skills}

linkedin_skills <- linkedin_keywords |> select(jobdesc_id,source, token_id,token,upos) |> 
    filter(upos %in% c('NOUN','ADJ','PROPN')) |>
    rename(part_of_speech_tag=upos) 
indeed_skills <- indeed_keywords |> select(jobdesc_id,source, token_id,token,upos) |> 
    filter(upos %in% c('NOUN','ADJ','PROPN')) |>
    rename(part_of_speech_tag=upos)

job_skills <- union_all(linkedin_skills,indeed_skills)

```


#### Write tables into job_desc_data schema

```{r}

dbWriteTable(local_db, name="job_descriptions", value=final_jds,field.types = c(jobdesc_id='int',source='text',job_title="text",company_id='int', link="text",location='text',employment_type='text',job_function='text',salary='text',seniority_level='text'), row.names=FALSE,append=TRUE)
dbWriteTable(local_db, name="company_information", value=company_info,field.types = c(company_id="text", company_name="text",industry_group='text'), row.names=FALSE,append=TRUE)
dbWriteTable(local_db, name="job_skills", value=job_skills,
             field.types = c(jobdesc_id="int",source="text",token_id='int',token='text',part_of_speech_tag='text'), row.names=FALSE,append=TRUE)


```


#### Pull queries to load data: example total skills per job description using parameterized schema


```{r}
query <-
paste('with jskills as (
SELECT j.jobdesc_id,j.source, count(distinct token) as total_skills
FROM ', params$dbschema, '.job_skills as j
GROUP BY j.jobdesc_id, j.source
 )
 
 SELECT c.company_name, d.job_title,d.source, j.total_skills
 FROM ', params$dbschema ,'.job_descriptions as d
 LEFT JOIN ',params$dbschema, '.company_information as c
 ON d.company_id = c.company_id
 LEFT JOIN jskills as j
 ON j.jobdesc_id = d.jobdesc_id and  j.source = d.source
 order by total_skills desc;')

jd_total_skills <- dbGetQuery(local_db, query)
head(jd_total_skills,n=10)
```




