---
title: "LinkedIn Salary Data Extraction"
author: "Andrew Bowen, Anthony Arroyo, Josh Forster, Ben Inbar"
date: "2022-10-22"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(rjson)
library(jsonlite)
library(stringr)
```

Reading in our [scraped linkedin job posting data](https://github.com/Anthogonyst/Team_Science/blob/master/data/job_description_data.json). Will need to extract the salary information contained within the `job_paragraphs` and `job_bullets` character fields.
```{r}
data_url <- "https://raw.githubusercontent.com/Anthogonyst/Team_Science/master/data/job_description_data.json"

df = jsonlite::fromJSON(data_url, simplifyDataFrame = TRUE, flatten=TRUE)

head(df)
```
Extracting salary listings from the job postings that include them. These are typically formatted with 3 digits (e.g., 100k or $100k). 
```{r}
df <- df %>%
        mutate(paragraph_salaries = str_extract(job_paragraphs, "\\$?\\d{3}k?")) %>%
        mutate(bullet_salaries = str_extract(job_bullets, "\\$?\\d{3}k?"))

df %>% select(paragraph_salaries, bullet_salaries)
```

These aren't perfect values, a lot of job listings we scraped don't post salary info. In addition, our regex picks up some 401k values, which are not salary values

```{r}
# Replacing 401k with

df$paragraph_salaries = str_replace(df$paragraph_salaries, "401k?", "")
df$bullet_salaries = str_replace(df$bullet_salaries, "401k?", "")

df$paragraph_salaries = as.numeric(df$paragraph_salaries)
df$bullet_salaries = as.numeric(df$bullet_salaries)

head(df)
```
```{r}
df$paragraph_salaries
```



```{r}
ggplot(df, aes(x=paragraph_salaries)) + geom_histogram()
```